\documentclass{article}

\usepackage{amsmath}
\usepackage{parskip}
\usepackage{tikz}
\renewcommand{\emph}{\textbf}
\renewcommand{\bar}{\overline}
\DeclareMathOperator{\Log}{Log}
\DeclareMathOperator{\Arg}{Arg}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\csch}{csch}

\begin{document}

\section{Frame 37 -- Derivatives with Real Variables}
\subsection{Definition}
In the previous chapter, we looked at derivatives of complex functions of a complex variable $z$. Now, we look at the derivatives of a complex-valued function of a real variable $t$. If we write our function as
\[
	w(t) = u(t) + iv(t)
\]
where $u$ and $v$ are real-valued, then we can define the derivative of $w$ at a point $t$ as
\[
	w'(t) = \frac{d}{dt} w(t) = u'(t) + iv'(t)
\]
provided that $u'$ and $v'$ exist at $t$.

\subsection{Properties}
If $z_0 = x_0 + iy_0$ is a complex constant, then we can show that
\begin{align*}
	\frac{d}{dt} [z_0 w(t)]
	&= [(x_0 + iy_0)(u(t) + iv(t)]' \\
	&= [x_0 u(t) - y_0 v(t)]' + i[y_0 u(t) + x_0 v(t)]' \\
	&= [x_0 u'(t) - y_0 v'(t)] + i[y_0 u'(t) + x_0 v'(t)] \\
	&= z_0 w'(t)
\end{align*}
as we expect.

Next, if $z_0$ is still a complex constant, the derivative of $e^{z_0 t}$ is
\begin{align*}
	\frac{d}{dt} e^{z_0 t} 
	&= \frac{d}{dt} e^{x_0 t}(\cos y_0 t + i sin y_0 t) \\
	&= \frac{d}{dt} e^{x_0 t} \cos y_0 t + i \frac{d}{dt} e^{x_0 t} \sin y_0 t \\
	&= (x_0 + iy_0)(e^{x_0 t} \cos y_0 t + ie^{x_0 t} \sin y_0 t) \\
	&= z_0 e^{z_0 t}
\end{align*}

Many other rules carry over from standard calculus. However, some rules no longer apply. For instance, in calculus, the mean value theorem for derivatives states that
\[
	w'(c) = \frac{w(b) - w(a)}{b - a}
\]
for some $c$ in the interval $a \le c \le b$ as long as $w$ is continuous. However, this is easily disproved by the function
\[
	w(t) = e^{it}
\]
If $a = 0$ and $b = 2\pi$, then $w(a) = w(b) = 1$ and we expect to find a point $c$ in $[0, 2\pi]$ such that $w'(c) = 0$. However, no such points exist -- the magnitude of the derivative is always $1$.


\clearpage
\section{Frame 38 -- Definite Integrals of Complex Functions}
\subsection{Definitions}
If $w(t)$ is a complex-valued function of a real variable $t$, as in the previous section
\[
	w(t) = u(t) + iv(t)
\]
then we define the \emph{definite integral} of $w(t)$ over the interval $a \le t \le b$ as
\[
	\int_a^b w(t) dt = \int_a^b u(t) dt + i \int_a^b v(t) dt
\]
provided the two right-side integrals exist. Then,
\begin{align*}
	\Re\left[\int_a^b w(t)dt\right] &= \int_a^b \Re[w(t)] dt \\
	\Im\left[\int_a^b w(t)dt\right] &= \int_a^b \Im[w(t)] dt
\end{align*}
Improper integrals over unbounded intervals are defined similarly.

The two real integrals will exist as long as $u$ and $v$ are \emph{piecewise continuous} on the interval $[a, b]$ -- that is, continuous everywhere in the interval except possibly for a finite number of points where it has one-sided limits. When $u$ and $v$ are piecewise continuous, we say that $w$ is also piecewise continuous.

\subsection{Properties}
The most common rules of integrals from calculus apply here as well:
\begin{itemize}
	\item $\int z_0 w(t)dt = z_0 \int w(t)$
	
	\item $\int w_1(t) + w_2(t)dt = \int w_1(t)dt + \int w_2(t)dt$
	
	\item $\int_a^b w(t) dt = -\int_b^a w(t) dt$
	
	\item $\int_a^b w(t) dt = \int_a^c w(t) dt + \int_c^b w(t) dt$
\end{itemize}

We can also extend the fundamental theorem of calculus to complex integrals. Suppose that two functions
\begin{align*}
	w(t) &= u(t) + iv(t) \\
	W(t) &= U(t) + iV(t) 
\end{align*}
are continuous on the interval $[a, b]$ and $W'(t) = w(t)$ when $a \le t \le b$. Then, we can write
\[
	\int_a^b w(t) dt = W(b) - W(a) = W(t) \Big|_a^b 
\] 

\textit{Example: noting that the derivative of $\frac{1}{i} e^{it}$ is
\[
	\frac{d}{dt} \left( \frac{1}{i} e^{it} \right)
	= \frac{1}{i} ie^{it}
	= e^{it}
\]
we can evaluate $\int e^{it} dt$ as
\begin{align*}
	\int_0^{\pi/4} e^{it} dt 
	&= \frac{e^{it}}{i} \Big|_0^{\pi/4} \\
	&= \frac{1}{i} \left[ e^{\pi/4} - 1 \right] \\
	&= \frac{1}{i} \left[ \frac{1}{\sqrt{2}} - 1 + \frac{i}{\sqrt{2}} \right] \\
	&= \frac{1}{\sqrt{2}} + i\left( 1 - \frac{1}{\sqrt{2}} \right)
\end{align*}}

As in the previous section, the mean value theorem for integrals does not apply. We can show this by finding the integral $\int_0^{2\pi} e^{it} dt = 0$, even though the function is never zero on this interval.


\clearpage
\section{Frame 39 -- Contours}
\subsection{Definitions}
In calculus, integrals are defined on intervals of the real line. In complex analysis, we instead use curves in the complex plane.

An \emph{arc} is a set of points $z = (x, y)$ in the complex plane such that the functions
\[
	x = x(t),	\quad y = y(t);	\quad z = z(t) = x(t) + iy(t)
\]
are continuous functions of the parameter $t$, where $a \le t \le b$. This definition is a continuous mapping of the interval $a \le t \le b$ into the $z$ plane.

We say that an arc is \emph{simple} if it does not cross itself; ie:
\[
	z(t_1) \ne z(t_2)	\quad \text{for all } t_1 \neq t_2
\]
If a simple arc starts and ends at the same point ($z(a) = z(b)$), it is called a \emph{simple closed curve}. These curves are \emph{positively oriented} when they are oriented in the counterclockwise direction. 

\textit{Example: the unit circle
\[
	z = e^{i\theta}
\]
where $0 \le \theta \le 2\pi$ is a positively oriented simple closed curve centered at the origin with a radius of $1$. A more general circle is
\[
	z = z_0 + Re^{i\theta}
\]
which is centered at $z_0$ and has a radius of $R$.}

\subsection{Uniqueness}
Note that the parametric representation for any arc is not unique. If we know a function $\phi$ such that
\[
	t = \phi(\tau)
\]
maps the interval $\alpha \le \tau \le \beta$ onto the interval $a \le t \le b$. Then, the two equations
\[
	z(t) \quad (a \le t \le b)
\]
and
\[
	z(\phi(t)) \quad	(\alpha \le t \le \beta)
\]
represent the same arc.

\subsection{Smoothness}
Suppose that the real and imaginary components of $z$ are differentiable, and their derivatives are continuous. Then, the arc $z(t)$ is a \emph{differentiable arc}, and
\[
	|z'(t)| = |x'(t) + iy'(t)| = \sqrt{[x'(t)]^2 + [y'(t)]^2}
\]
is integrable. This allows us to find the length of an arc as
\[
	L = \int_a^b |z'(t)| dt
\]

If an arc is differentiable and $z'(t)$ is never zero (except maybe at $t = a$ or $t = b$), then we call the arc a \emph{smooth arc}. We can write the unit tangent vector
\[
	\mathbf{T} = \frac{z'(t)}{|z'(t)|}
\]
which has an angle of inclination of $\arg z'(t)$. 

A \emph{contour} is an arc which consists of a finite number of smooth arcs joined together. Specifically, if $z(t)$ represents a contour, then $z(t)$ is continuous and $z'(t)$ is piecewise continuous. If a contour is also a simple closed arc, we call it a \emph{simple closed contour}. 

The points on a simple closed arc are the boundary points of two different domains:
\begin{itemize}
	\item The interior of the arc, which is bounded;
	\item The exterior of the arc, which is unbounded.
\end{itemize}


\clearpage
\section{Frame 40 -- Contour Integrals}
\subsection{Definitions and conditions}
We can now integrate a complex function $f$ along a contour $C$, which starts and ends at points $z_1$ and $z_2$, respectively. This is effectively a line integral. These integrals can be written as
\[
	\int_C f(z) dz
\]
or, if the integral does not depend on the path taken,
\[
	\int_{z_1}^{z_2} f(z) dz
\]

This integral (along a complex path) represents an integral with respect to a real parameter $t$. If the contour $C$ is written as $z(t)$ on the interval $a \le t \le b$, then the integral represented is
\[
	\int_C f(z) dz = \int_a^b f[z(t)] z'(t) dt
\]
Since $z'(t)$ must be piecewise continuous, this integral exists as long as $f[z(t)]$ is also piecewise continuous on this interval.

\subsection{Basic properties}
From the definition and the properties of integrals, we can write
\[
	\int_C z_0 f(z) dz = z_0 \int_C f(z) dz
\]
and
\[
	\int_C [f(z) + g(z)] dz = \int_C f(z) dz + \int_C g(z) dz
\]
We can also create a new contour $-C$ that consists of the points in $C$ in reversed order -- this contour extends from $z_2$ to $z_1$. Integrating along this reversed contour, we find that
\begin{align*}
	\int_-C f(z) dz 
	&= \int_{-b}^{-a} f[z(-t)] \frac{d}{dt} z(-t) dt \\
	&= -\int_{-b}^{-a} f[z(-t)] z'(-t) dt \\
	&= -\int_a^b f[z(t)] z'(t) dt \\
	&= -\int_C f(z) dz
\end{align*}
We can also split up a contour $C$ into multiple legs $C_1, C_2, \dots$. If we can write a contour this way, then we say that $C = C_1 + C_2$. The contour integral along $C$ can then be written as
\[
	\int_C f(z) dz = \int_{C_1} f(z) dz + \int_{C_2} f(z) dz
\]


\clearpage
\section{Frame 41 -- Examples of Contour Integrals}
This section will show several specific examples of contour integrals.

\subsection{Example 1}
Suppose that the contour $C$ is the right hand half of the circle $|z| = 2$:
\[
	z = 2e^{i\theta},	\quad \left( -\frac{\pi}{2} \le \theta \le \frac{\pi}{2}\right)
\]
Then,
\begin{align*}
	\int_C \bar{z} dz
	&= \int_{-\pi/2}^{\pi/2} \bar{2e^{i\theta}} (2e^{i\theta})' d\theta \\
	&= 4i\int_{-\pi/2}^{\pi/2} e^{-i\theta} e^{i\theta} d\theta \\
	&= 4i\int_{-\pi/2}^{\pi/2} d\theta \\
	&= 4\pi i
\end{align*}
Also, note that all of the points on this semicircle satisfy
\[
	z \bar{z} = |z|^2 = 4
\]
so we can see from this result that
\[
	\int_C \frac{1}{z} dz = \pi i
\]

\subsection{Example 2}
Suppose that the points $O$, $A$, and $B$ are $0$, $i$, and $1 + i$, respectively. Then, if $C_1$ is the polyline $OAB$ and
\[
	f(z) = y - x - i3x^2
\]
then the contour integral of $f$ along $C_1$ is
\begin{align*}
	\int_{C_1} f(z) dz
	&= \int_{OA} f(z) dz + \int_{AB} f(z) dz \\
	&= \int_0^1 yi dy + \int_0^1 (1 - x - i3x^2) dx \\
	&= \frac{i}{2} + \int_0^1 (1 - x)dx - 3i\int_0^1 x^2 dx \\
	&= \frac{i}{2} + \frac{1}{2} - i \\
	&= \frac{1 - i}{2}
\end{align*}

Next, if $C_2$ is the line $OB$, the contour integral along this curve is
\begin{align*}
	\int_{C_2} f(z) dz 
	&= \int_0^1 -i3x^2(1 + i)dx \\
	&= 3(1 - i) \int_0^1 x^2 \\
	&= 1 - i
\end{align*}

Finally, the integral of $f$ over the simple closed contour $OABO$ is $C_1 - C_2$, which is
\[
	\int_{OABO} f(z) dz = \frac{-1 + i}{2}
\]

\subsection{Example 3}
Suppose that $C$ is any arbitrary smooth arc from a fixed point $z_1$ to another point $z_2$:
\[
	z = z(t)	\quad (a \le t \le b)
\]
The contour integral of $f(z) = z$ along this curve is
\begin{align*}
	\int_C z dz 
	&= \int_a^b z(t) z'(t) dt \\
	&= \int_a^b \frac{d}{dt} \frac{[z(t)]^2}{2} dt \\
	&= \frac{[z(t)]^2}{2} \Big|_a^b \\
	&= \frac{z_2^2 - z_1^2}{2}
\end{align*}
Note that this integral only depends on the endpoints of $C$ and not the path. This lets us write
\[
	\int_{z_1}^{z_2} z dz = \frac{z_2^2 - z_1^2}{2}
\]
This holds when $C$ is not a smooth contour. Since all contours are sums of finite numbers of smooth arcs, this expression holds for each arc in $C$, leading to the same final expression.

Also, note that the integral of $f(z) = z$ around any closed contour in the plane is zero.


\clearpage
\section{Frame 42 -- Examples with Branch Cuts}
A contour integral's path can include a point on a branch cut. The following two examples show this.

\subsection{Example 1}
Suppose we want to integrate the function 
\[
	f(z) = z^{1/2} = e^{\frac{1}{2} \log z}	\quad (0 < \arg z < 2\pi)
\]
on the semicircle
\[
	z = 3e^{i\theta}	\quad(0 \le \theta \le \pi)
\]
Although the function is not defined at $\theta = 0$, we can still write
\[
	f[z(\theta)] = e^{\frac{1}{2}(\ln 3 + i\theta)} = \sqrt{3} e^{i\theta/2}
\]
and the right hand limit of this function exists at $\theta = 0$. Thus, the integrand exists as long as we define the missing point as
\[
	f[z(0)] z'(0) = i3\sqrt{3}
\]
Then,
\begin{align*}
	\int_C f(z) dz 
	&= 3\sqrt{3} \int_0^\pi e^{i3\theta / 2} \\
	&= 3\sqrt{3} \frac{2}{3i} e^{i3\theta / 2} \Big|_0^\pi \\
	&= -\frac{2}{3i} (1 + i) \\
	&= -2\sqrt{3}(1 + i)
\end{align*}


\subsection{Example 2}
Suppose that we want to integrate the function
\[
	f(z) = z^{a - 1} = e^{(a - 1) \Log z} \quad (-\pi < \Arg z < \pi)
\]
on the positively oriented circle
\[
	z = Re^{i\theta}	\quad (-\pi \le \theta \le \pi)
\]
The contour integral is
\begin{align*}
	\int_C z^{a - 1} dz
	&= \int_{-\pi}^{\pi} iR^ae^{ia\theta} d\theta \\
	&= iR^a \int_{-\pi}^{\pi} e^{ia\theta} d\theta \\
	&= iR^a \left( \frac{e^{ia\theta}}{ia} \right)_{-\pi}^{\pi} \\
	&= i\frac{2R^a}{a} \frac{e^{ia\pi} - e^{-ia\pi}}{2i} \\
	&= i\frac{2R^a}{a} \sin a\pi
\end{align*}
Note that if $a$ is a non-zero integer, this integral is zero; if $a = 0$, this integral reduces to
\[
	\int_C \frac{dz}{z} = 2\pi i
\]


\clearpage
\section{Frame 43 -- Upper Bounds for Contour Integrals}
We can put a bound on the modulus of a contour integral by observing that
\[
	\left| \int_a^b w(t) dt \right| 
	\le \int_a^b \left| w(t) \right| dt
\]

\subsection{Theorem}
Suppose that $C$ is a contour with a length of $L$ and that $f(z)$ is a function that is piecewise continuous on $C$. If $M \ge 0$ is a real constant such that
\[
	|f(z)| \le M
\]
for all points on $C$, then
\[
	\left| \int_C f(z) dz \right| \le ML
\]
Note that such a number $M$ will always exist because $f$ is continuous on $C$.

\subsection{Examples}
\textit{Example: Suppose that
\[
	f(z) = \frac{z + 4}{z^3 - 1}
\]
and the contour $C$ is a quarter circle with a radius of $2$ in the first quadrant (running from $z = 2$ to $z = 2i$). Since $|z| = 2$ at all points on this contour, we can write that
\[
	|z + 4| \le |z| + 4 = 6
\]
and
\[
	|z^3 - 1| \ge |z|^3 - 1 = 7
\]
Since the length of the contour is $L = \pi$, we can write the upper bound
\[
	\left| \int_C \frac{z + 4}{z^3 - 1} dz \right| \le \frac{6\pi}{7}
\]
}

\textit{Example: suppose that $C_R$ is the semicircular contour
\[
	z = Re^{i\theta}	\quad	(0 \le \theta \le \pi)
\]
and $f$ is the function
\[
	f(z) = \frac{z^{1/2}}{z^2 + 1}
\]
where $z^{1/2}$ denotes the branch $-\pi/2 < \theta < 3\pi/2$. Anywhere on this semicircle,
\[
	|z^{1/2}| = \sqrt{R}
\]
and
\[
	|z^2 + 1| \ge ||z^2| - 1| = R^2 - 1
\]
Since the contour has a length of $\pi R$, the contour integral of $f$ along $C$ can be limited by
\begin{align*}
	\int_C f(z) dz 
	&\le \frac{\sqrt{R}}{R^2 - 1} \cdot \pi R \\
	&= \frac{\pi R^{3/2}}{R^2 - 1} \\
	&= \frac{\pi / \sqrt{R}}{1 - (1 / R^2)}
\end{align*}
As $R$ approaches infinity, this bound approaches zero, so
\[
	\lim_{R \to \infty} \int_C f(z) dz = 0
\]}


\clearpage
\section{Frame 44 -- Antiderivatives}
We saw earlier that some functions have integrals from $z_1$ to $z_2$ that are independent of path. This section will look more closely at such functions to extend the fundamental theorem of calculus.

\subsection{Antiderivatives and their theorem}
Recall that an antiderivative of a continuous function $f(z)$ on a domain $D$ is an analytic function $F(z)$ such that $F'(z) = f(z)$ for all $z$ in $D$. Also, note that antiderivatives are unique to an additive constant: if $F(z)$ and $G(z)$ are two antiderivatives of the same function, then $F'(z) - G'(z) = 0$, so $F(z) - G(z)$ must be constant everywhere.

The following theorem makes several relationships between antiderivatives and their properties.

\textit{Theorem: If $f(z)$ is a continuous function on a domain $D$, then any one of these statements implies the other two:
\begin{enumerate}
	\item $f(z)$ has an antiderivative $F(z)$ throughout $D$;
	\item Any integral of $f(z)$ along a contour in $D$ is path independent, and
	\[
		\int_{z_1}^{z_2} f(z) dz = F(z_2) - F(z_1)
	\]
	\item The integral of $f(z)$ around any closed contour in $D$ is zero. 
\end{enumerate}}

\subsection{Examples}
\textit{Example 1: the function $f(z) = z^2$ has an antiderivative $F(z) = z^3/3$ throughout the entire plane. This allows us to write, for any contour extending from $z = 0$ to $1 + i$,
\begin{align*}
	\int_0^{1+i} z^2 dz 
	&= \frac{z^3}{3} \Big|_0^{1+i} \\
	&= \frac{1}{3}(1 + i)^3 \\
	&= \frac{1}{3} (\sqrt{2} e^{i\pi/4} \\
	&= \frac{2}{3} \sqrt{2} e^{i3\pi/4} \\
	&= \frac{2}{3} (-1 + i)
\end{align*}}


\textit{Example 2: the function $f(z) = \frac{1}{z^2}$ is continuous everywhere except for the point $z = 0$. In this domain, it has an antiderivative $F(z) = \frac{-1}{z}$. Thus, if $C$ is a positively oriented circle centered at the origin,
\[
	\int_C \frac{dz}{z^2} = 0
\]}

\textit{Example 3: the function $f(z) = \frac{1}{z}$ does not have a simple antiderivative on the entire plane. Although $\log z$ is an antiderivative where it is defined, it requires a branch cut to be single valued.}

\textit{Suppose we want to evaluate the integral
\[
	\int_C \frac{dz}{z} 
\]
where $C$ is the full circle
\[
	z = 2e^{i\theta},	\quad -\frac{\pi}{2} \le \theta \le \frac{3\pi}{2}
\]
We can do this by splitting the contour into two legs: $C_1$ is the right semicircle ($-\pi/2 \le \theta \le \pi/2$) and $C_2$ is the left semicircle ($\pi/2 \le \theta \le 3\pi/2$). Then, the principal branch of the logarithm is a suitable antiderivative for $C_1$, so
\[
	\int_{C_1} \frac{dz}{z}
	= \Log(2i) - \Log(-2i) 
	= (\ln 2 + i\pi/2) - (\ln 2 - i\pi/2)
	= i\pi
\]
To evaluate the integral along $C_2$, we switch to the branch $0 < \theta < 2\pi$. Here,
\[
	\int_{C_2} \frac{dz}{z}
	= \log(-2i) - \log(2i)
	= (\ln 2 + i3\pi/2) - (\ln 2 + i\pi/2) 
	= i\pi
\]
so, adding these up,
\[
	\int_C \frac{dz}{z}
	= \int_{C_1} \frac{dz}{z} + \int_{C_2} \frac{dz}{z} 
	= i \pi + i \pi
	= 2\pi i
\]}

\textit{Example 4: suppose we want to evaluate the integral
\[
	\int_{-3}^{3} z^{1/2} dz
\]
where $z^{1/2}$ denotes the branch for $0 < \theta < 2\pi$ and we use any contour that is always above the real axis (except at the endpoints). Since this branch is not defined at the endpoints, we can replace the integrand with the branch
\[
	z^{1/2} = \sqrt{r} e^{i\theta/2}
	\quad (-\frac{\pi}{2} < \theta < \frac{3\pi}{2})
\]
This new function has an antiderivative of $\frac{2}{3} z^{3/2}$, so we can write
\[
	\int_{-3}^{3} z^{1/2} dz
	= R^{3/2} e^{i3\theta/2} \Big|_{-3}^3
	= 2\sqrt{3} (e^0 - e^{i3\pi/2})
	= 2\sqrt{3} (1 + i)
\]	
We could evaluate the same integral for any contour below the real axis in a similar manner.}


\clearpage
\section{Frame 46 -- Cauchy-Goursat Theorem}
\subsection{The theorem}
We will show some simple conditions under which a contour integral is guaranteed to be zero.

Suppose that $C$ is a simple, closed, positively-oriented contour $z(t)$ (where $a \le t \le b$) and $f$ is a function that analytic at each point interior to and on $C$. Then, we can write
\[
	\int_C f(z) dz = \int_a^b f[z(t)] z'(t) dt
\]
Then, if
\[
	f(z) = u(x, y) + iv(x, y) 
\]
and
\[
	z(t) = x(t) + iy(t)
\]
we can write this integral as
\[
	\int_C f(z) dz = \int_C u dx - v dy + i\int_C v dx + u dy
\]
We can then use Green's theorem to write these line integrals as double integrals over the region $R$ bounded by $C$:
\[
	\int_C f(z) dz 
	=  \int \int_R (-v_x - u_y) dA 
	+ i\int \int_R  (u_x - v_y) dA 
\]
Finally, due to the Cauchy Riemann equations, both of these integrands are zero, so
\[
	\int_C f(z) dz = 0
\]
whenever $f$ is analytic and $f'$ is continuous in $R$. Note that, due to Goursat, the continuity condition is actually unnecessary.

\subsection{Example}
\textit{Example: if $C$ is a simple closed contour, then
\[
	\int_C e^{z^3} dz = 0
\]	
since $e^{z^3}$ is analytic everywhere.}


\clearpage
\section{Frame 48 -- Simply Connected Domains}
The conditions on the contour in the previous section can be relaxed when the domain of interest is simply connected. The following theorem is an adapted version:

\textit{Theorem: if a function $f$ is analytic throughout a simply connected domain $D$, then
\[
	\int_C f(z) dz = 0
\]
for every closed contour $C$ (simple or not) in $D$.}

This is a simple extension of the theorem -- if a contour intersects itself a finite number of times, $k$, then the contour can be viewed as $k$ different simple and closed legs, which must all have an integral of zero. Thus,
\[
	\int_C f(z) dz = \sum_{i = 0}^{k} \int_{C_i} f(z) dz = 0
\] 

\textit{Example: if $C$ is any closed contour in the disk $|z| < 2$, then
\[
	\int_C \frac{ze^z}{(z^2 + 9)^5} dz = 0
\] because the only singularities of this function are outside the disk (at $z = \pm 3i$).}

Note that this implies, from the theorem earlier in the chapter, that \textit{every entire function has an antiderivative everywhere}.


\clearpage
\section{Frame 49 -- Multiply Connected Domains}
We can further adapt the Cauchy-Goursat theorem to be useful on multiply connected domains.

\subsection{Extended theorem}
\textit{Theorem: Suppose that
\begin{itemize}
	\item $C$ is a simple, closed, positively oriented contour 
	\item $C_k$ are simple, closed, negatively oriented contours interior to $C$ that do not overlap (interiors and contours are disjoint)
\end{itemize}
If a function $f$ is analytic on each contour and the multiply connected domain inside $C$ but outside $C_k$, then
\[
	\int_C f(z) + \sum_{k=1}^n \int_{C_k} f(z) dz = 0
\]}

Note that the multiply connected domain is to the left of each contour.

\subsection{Applications and examples}
A corollary of this extended theorem follows.

\textit{Corollary: if $C_1$ and $C_2$ are two positively oriented contours such that $C_1$ is contained inside $C_2$, then for any function $f$ analytic inside $C_2$,
\[
	\int_{C_2} f(z) dz + \int_{-C_1} f(z) dz = 0
\]
so
\[
	\int_{C_2} f(z) dz = \int_{C_1} f(z) dz
\]}

\textit{Example: if $C$ is any positively-oriented, simple, closed contour that encloses the origin, then we can make positively oriented circular contour $C_0$ that is entirely inside $C$ and contains the origin. We've shown before that
\[
	\int_{C_0} \frac{dz}{z} = 2\pi i
\]
so
\[
	\int_C \frac{dz}{z} = \int_{C_0} \frac{dz}{z} = 2\pi i
\]}


\clearpage
\section{Frame 50 -- The Cauchy Integral Formula}
\subsection{The theorem}
\textit{Theorem: if $C$ is a positively oriented simple closed contour, $f$ is analytic everywhere inside and on $C$, and $z_0$ is a point interior to $C$, then
\[
	f(z_0) = \frac{1}{2\pi i} \int_C \frac{f(z)}{z - z_0} dz
\]}

This theorem effectively says that an analytic function's values inside a contour are completely determined by the function's values \emph{on} the contour. Notice that we can rearrange this formula as
\[
	\int_C \frac{f(z)}{z - z_0} dz = 2\pi i f(z_0)
\]
to evaluate the values of some contour integrals.

\subsection{Example}
\textit{Example: Suppose that $C$ is the positively oriented circle $|z| = 2$ and $f$ is the function
\[
	f(z) = \frac{z}{9 - z^2}
\]
To evaluate the integral of $f(z) / (z + i)$ around this contour, we can write
\[
	\int_C \frac{f(z)}{z + i} dz
	= 2\pi i f(-i)
	= 2\pi i \left( \frac{-i}{10} \right)
	= \frac{\pi}{5}
\]}


\clearpage
\section{Frame 51 -- An Extension}
\subsection{Extending Cauchy's formula}
We can extend the Cauchy integral formula to find the derivatives of $f$ at a point. If we use the same conditions as before ($C$ is positively oriented, simple, and closed; $f$ is analytic inside and on $C$), then the Cauchy integral formula states that
\[
	f(z) = \frac{1}{2\pi i} \int_C \frac{f(s)}{s - z} ds
\]
where $z$ is a point inside $C$ and $s$ denotes points on $C$. If we differentiate both sides of this expression with respect to $z$, we find that
\[
	f'(z) = \frac{1}{2\pi i} \int_C \frac{f(s)}{(s - z)^2} ds
\]
The same technique can be used to verify that
\[
	f''(z) = \frac{1}{\pi i} \int_C \frac{f(s)}{(s - z)^3} ds
\]	
and, in general,
\[
	f^{(n)}(z) = \frac{n!}{2\pi i} \int_C \frac{f(s)}{(s - z)^{n+1}} ds
\]

Alternatively, this formula can be written in the form
\[
	\int_C \frac{f(z)}{(z - z_0)^{n+1}} = \frac{2\pi i}{n!} f^{(n)}(z_0)
\]

\subsection{Examples}
\textit{Example 1: suppose that $C$ is the positively oriented unit circle $|z| = 1$. Then, if we write $f(z) = e^{2z}$, we can find that
\[
	\int_C \frac{e^{2z}} z^4 dz 
	= \int_C \frac{f(z)}{(z - 0)^{3 + 1}} dz
	= \frac{2\pi i}{3!} f'''(0)
	= \frac{8\pi i}{3}
\]}

\textit{Example 2: suppose that $z_0$ is any point inside a positively-oriented simple contour $C$ and $f(z) = 1$. Then,
\[
	\int_C \frac{1}{z - z_0} dz = 2\pi i \cdot f(z_0) = 2\pi i
\]
and
\[
	\int_C \frac{1}{(z - z_0)^{n+1}} dz = 0
\]
for positive integers $n$.}


\clearpage
\section{Frame 52 -- Consequences of the Extension}
This section will cover some consequences of the theorems proves in the last two frames.

\subsection{Derivatives are analytic}
\textit{Theorem: if a function $f$ is analytic at a point, then its derivatives of all orders are also analytic there.}

To prove this, suppose that $f$ is analytic at a point $z_0$. This implies that it is analytic on some neighbourhood centered at $z_0$, so we can create a positively-oriented circle $C_0$ centered at $z_0$ such that $f$ is analytic in and on $C_0$. Then, we know that
\[
	f''(z) = \frac{1}{\pi i} \int_{C_0} \frac{f(s)}{(s - z)^3} ds
\]
so the second derivative exists, and the first derivative must be analytic. These steps can be repeated to show analyticity of any order of derivative, so every derivative $f^{(n)}$ is analytic at $z_0$.

Note that this also implies that, if an analytic function can be written as
\[
	f(z) = u(x, y) + iv(x, y)
\]
then, since all derivatives of $f$ exist, the components $u$ and $v$ have continuous partial derivatives of all orders at $(x_0, y_0)$.

\subsection{Contour integrals and analyticity} 
\textit{Theorem: suppose that $f$ is continuous on a domain $D$. Then, if
\[
	\int_C f(z) dz = 0
\]
for every closed contour $C$ in $D$, then $f$ is analytic on $D$.}

Proof: if this contour integral is always zero, then $f$ must have an antiderivative $F$ in $D$. However, since $f$ is the derivative of $F$, we know from the previous theorem that $f$ must be analytic, so we are done.

\subsection{Bounds for derivatives}
\textit{Theorem (Cauchy's Inequality): suppose that $C_R$ is a positively-oriented circle centered at $z_0$ with a radius of $R$ and $f$ is a function that is analytic in and on $C_R$. If
\[
	|f(z)| \le M_R
\]
on $C_R$, then
\[
	|f^{(n)}(z_0)| \le \frac{n! M_R}{R^n}
\]}

Proof: if $f$ is analytic in this closed domain, then
\[
	f^{(n)}(z_0) = \frac{n!}{2\pi i} \int_{C_R} \frac{f(z)}{(z - z_0)^{n+1}} dz
\]
The numerator and denominator of this integrand satisfy
\[
	|f(z)| \le M_R
\]
and
\[
	|(z - z_0)^{n+1}| = R^{n+1}
\]
so
\[
	|f^{(n)}(z_0)| 
	\le \left|\frac{n!}{2\pi i}\right| \cdot \frac{M_R}{R^{n+1}} \cdot 2\pi R
	= \frac{n! M_R}{R^n}
\]


\clearpage
\section{Frame 53 -- Liouville's Theorem \& The Fundamental Theorem of Algebra}
\subsection{Liouville's Theorem}
No entire function is bounded in the complex plane except for a constant. This is stated in the following theorem:

\textit{Theorem: if a function $f$ is entire and bounded in the complex plane, then $f(z)$ is constant throughout the plane.}

To show this, suppose that $f$ is bounded such that $|f(z)| \le M$ for all $z$. Then, Cauchy's inequality states that
\[
	|f'(z_0)| \le \frac{M}{R}
\]
This must also hold as $R$ gets arbitrarily large, so $f'(z) = 0$ everywhere, and the function must be constant. 

\subsection{The fundamental theorem of algebra}
We can derive the following theorem from Liouville's theorem:

\textit{Theorem: any polynomial has at least one zero. That is, if
\[
	P(z) = a_0 + a_1 z + a_2 z^2 + \dots + a_n z^n
\]
then there exists at least one point $z_0$ such that $P(z_0) = 0$.}

To show this, suppose that $P(z)$ is never zero. Then, the function
\[
	f(z) = \frac{1}{P(z)}
\]
is bounded over the entire plane. However, this implies that $f(z)$ is constant, and $P(z)$ is constant. This is a contradiction -- $P(z)$ is not constant -- so $P(z)$ must have at least one zero.

Extending this theorem, we can write any polynomial in the form
\[
	P(z) = c(z - z_1)(z - z_2) \dots (z - z_n)
\]
This means that $P(z)$ can have no more than $n$ distinct zeros. It may have less -- it is possible for some of these constants $z_k$ to be the same.


\clearpage
\section{Frame 54 -- Maximum Modulus Principle}
\subsection{Lemma: constant functions}
The following lemma will be helpful in the following subsection:

\textit{Lemma: $f$ is analytic in a neighbourhood of $z_0$ and $|f(z)| \le |f(z_0)|$ for all $z$ in this neighbourhood, then $f(z) = f(z_0)$ throughout the neighbourhood.}

Suppose that we find the value of $f(z_0)$ using Cauchy's integral formula with the contour $z = z_0 + \rho e^{i\theta}$:
\[
	f(z_0) = \frac{1}{2\pi i} \int_{C_\rho} \frac{f(z)}{z - z_0} dz
\]
Substituting the contour's equations in, we find that
\[
	f(z_0) = \frac{1}{2\pi i} \int_0^{2\pi} 
		\frac{f(z_0 + \rho e^{i\theta})}{\rho e^{i\theta}} 
		\cdot i\rho e^{i\theta} d\theta
	= \frac{1}{2\pi} \int_0^{2\pi} f(z_0 + \rho e^{i\theta}) d\theta
\]
From this, we see that
\[
	|f(z_0)| \le \frac{1}{2\pi} \int_0^{2\pi} |f(z_0 + \rho e^{i\theta})| d\theta
\]
However, $|f(z_0 + \rho e^{i\theta})| \le |f(z_0)|$, so we can extend this to
\begin{align*}
	|f(z_0)| 
	&\le \frac{1}{2\pi} \int_0^{2\pi} |f(z_0 + \rho e^{i\theta})| d\theta \\
	&\le \frac{1}{2\pi} \int_0^{2\pi} |f(z_0)| d\theta \\
	&= |f(z_0)|
\end{align*}
Since the beginning and ending terms of this inequality are equal, we see that the two integrals are equal. Their integrands must also be equal, so
\[
	|f(z_0 + \rho e^{i\theta})| = |f(z_0)|
\]
This holds as long as the point $z_0 + \rho e^{i\theta}$ is in the neighbourhood. Thus, $|f(z)|$ is constant in this neighbourhood, so $f(z)$ must also be constant, with the value of $f(z_0)$.

\subsection{The maximum modulus principle}
We can use the previous lemma to prove the maximum modulus principle.

\textit{Theorem: if an analytic function $f$ is not constant in a domain $D$, then $|f(z)|$ has no maximum value in $D$.}

Suppose that the modulus of $f$ has a maximum value $|f(z_0)|$. Then, we can draw a neighbourhood $N_0$ at $z_0$ over which the function must be constant (due to the previous lemma). To be precise, the function has the value $f(z_0)$ over this entire neighbourhood.

Then, we can choose any point $z_1 \ne z_0$ in the neighbourhood $N_0$ and draw another neighbourhood $N_1$ around it. Since $|f(z_1)| = |f(z_0)|$, $f$ must also be constant on $N_1$; as above the function has a value of $f(z_1) = f(z_0)$ over this entire neighbourhood.

This process can be repeated to reach any point $P$ in the domain. In this manner, we will eventually find that $f(P) = f(z_0)$ for all points $P$ in $D$, so the function is constant on $D$.

\subsection{Closed regions}
The previous theorem can be used to state a simple corollary:

\textit{Corollary: if $f$ is continuous on a closed, bounded region $R$ and both analytic and non-constant on the interior of $R$. Then, the maximum value of $|f(z)|$ in $R$, which will always be reached at one or more points, can only occur on the boundary of $R$.}

Note that, if we write a function in terms of its components 
\[
	f(z) = u(x, y) + iv(x, y),
\]
then the component function $u(x, y)$ must also be maximized on the boundary of $R$ and not on the interior. This comes from the fact that the function
\[
	g(z) = e^{f(z)}
\]
must have a modulus |g(z)| that is maximum on the boundary. Since the modulus is $\exp{u(x, y)}$, this implies that $u$ is also maximum here.

\subsection{Example}
\textit{Example: recall that the modulus of the function $f(z) = \sin z$ can be written as
\[
	|\sin z| = \sqrt{\sin^2 x + \sinh^2 y}
\]
If we consider the region $0 \le x \le \pi$, $0 \le y \le 1$, then we know that the modulus must be maximized on the boundary.}

\textit{We can find the maximum point by recognizing that $\sin^2 x$ is maximum at $x = \pi/2$ and $\sinh^2 y$ is maximum at $y = 1$, so $|\sin z|$ is maximum at the boundary point $z = (\pi / 2, 1)$.}
\end{document}